Beyond clines: lineages and haplotype blocks in hybrid zones

### 2016-04-26 drafts/supplement.tex
fixed S19 caption

\begin{figure}
    \includegraphics{figs/cond_freqs_comparison_tau_1280.pdf}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=1280$},
        as in figure \ref{sfig:condAlleleFreq_tau80_comparison}.
        Deviations are larger still than at $\tau=320$, 
        due to genetic drift.
    } \label{sfig:condAlleleFreq_tau1280_comparison}
\end{figure}
\clearpage
\begin{figure}
    \includegraphics{figs/s001_adjacentBlocksAlongChromAncBConditioning}
    \includegraphics{figs/s001_adjacentBlocksAlongChromNoConditioningHighRes}
        \caption{
     Normalized ancestry $B$ block lengths (top) and all ancestry block lengths (bottom) along chromosome under $s=0.001$ and other parameters as for Fig.~\ref{Fig:blockLengths}. } \label{sfig:blockLengthPlot_t1000_s0.001}
\end{figure}

>>>>

\begin{figure}
    \includegraphics{figs/cond_freqs_comparison_tau_1280.pdf}
    \caption{
        \textbf{Conditional frequencies of ancestry $A$ at $\tau=1280$},
        as in figure \ref{sfig:condAlleleFreq_tau80_comparison}.
        Deviations are larger still than at $\tau=320$, 
        due to genetic drift.
    } \label{sfig:condAlleleFreq_tau1280_comparison}
\end{figure}
\clearpage
\begin{figure}
    \includegraphics{figs/s001_adjacentBlocksAlongChromAncBConditioning}
    \includegraphics{figs/s001_adjacentBlocksAlongChromNoConditioningHighRes}
        \caption{
     Normalized ancestry $B$ block lengths (top) and all ancestry block lengths (bottom) along chromosome under $s=0.001$ and other parameters as for Fig.~\ref{Fig:blockLengths} ($\tau=1000,\sigma=1$). } \label{sfig:blockLengthPlot_t1000_s0.001}
\end{figure}
